---
title: "Five Years of Crashes in Victoria"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    source: embed
    theme: yeti
---

```{r setup, include=FALSE}
library(flexdashboard)
```
<!-- Leafly Map for fatal accidents -->
### Where are fatal accidents located?

```{r}
library(leaflet)
library(dplyr)
Crashes_Edited <- read.csv("~/R/Crashes_Edited.csv")
accidents_fatal <- Crashes_Edited %>% filter(FATALITY > 0)
leaflet(data = accidents_fatal) %>%
  addTiles() %>%
  addMarkers()
```

***

Fatal accidents are scattered throughout the state, however as expected, the amount of incidents are slightly more dense within the metropolitan area.

<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
Discover.data.vic.gov.au

<!-- Chart for most common accident types, ordering the accidents by most common to least -->
### What are the most common form of accidents? {data-padding=50}

```{r}
library(plotly)
Crashes_Edited <- read.csv("~/R/Crashes_Edited.csv")
Crashes_Edited$ACCIDENT_TYPE <- factor(Crashes_Edited$ACCIDENT_TYPE,levels = c( "Collision with vehicle", "Collision with a fixed object","Struck Pedestrian","No collision and no object struck","Vehicle overturned (no collision)", "Struck animal","collision with some other object", "Fall from or in moving vehicle", "Other accident"))
p <- ggplot(data = Crashes_Edited, aes(x = ACCIDENT_TYPE))+geom_bar() + facet_grid(rows = vars(STAT_DIV_NAME)) + ylab("Accident Count") + theme(axis.text.x = element_text(angle = 90), axis.title.x = element_blank(), axis.title.y = element_blank())
ggplotly(p)
```

***

Overall, the most common type of accident is a collision with a vehicle, with there being more of these collisions in the city. As expected, there are more collisions with pedestrians in the city.

<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
Discover.data.vic.gov.au

<!-- Accidents sorted by year, not including 2019 as it was not a complete year -->
### Has there been an increase in serious accidents?

```{r}
library(plotly)
Crashes_Edited <- read.csv("~/R/Crashes_Edited.csv")
Crashes_Non2019 <- Crashes_Edited %>% filter(ACCIDENT_YEAR < 2019)
Crashes_Non2019$SEVERITY <- factor(Crashes_Non2019$SEVERITY,levels = c("Fatal accident", "Serious injury accident", "Other injury accident", "Non injury accident"))
p1 <- ggplot(data = Crashes_Non2019, aes(x = SEVERITY, fill = SEVERITY)) + geom_bar() + facet_grid(~ ACCIDENT_YEAR) + theme(axis.text.x = element_blank(), axis.ticks = element_blank(), legend.title = element_blank(), axis.title.y = element_blank())+ scale_fill_manual(values = c("#2171b5", "#6baed6", "#bdd7e7","#eff3ff" ))
ggplotly(p1)
```

***
Initially there was an increase in all levels of accidents from 2013 - 2015. However, it appears that accidents in general are on a downward trend.

<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
Discover.data.vic.gov.au

<style type="text/css">

.sbframe-commentary {
   font-size: 15px;

</style>
